---
title: "Extra Credit Assignment - Angel Reese"
author: "Coco Donovan"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction: 
Angel Reese was a highly regarded recruit coming out of high school, but her 
first year of college was cut short by injury. In Reese's second year, she 
averaged a double-double in one of the premier conferences in the NCAA. Reese's
decided that she wanted a change of scenery for the rest of her college career, 
so she transferred to LSU. At LSU, had Reese matched her year-two production, 
she would be a lock for All-American, but in true Angel Reese style, she improved
yet again. Reese has had a double-double each game this season (in points and 
total rebounds), which has allowed her to set an SEC record once held by WNBA 
great Slyvia Fowles. Reese has become a leading contender for National Player of
the Year. And so, I chose to make Reese the focal subject of this extra credit 
assignment.

## Necessary Packages

```{r}
library(dplyr)
library(rvest)
library(tidyverse) 
```

## Downloading the data

```{r}
angel_url <- 'https://www.sports-reference.com/cbb/players/angel-reese-1/gamelog/2023/#gamelog.html'

angel <- angel_url %>%
  read_html()  %>%
  html_nodes('table') %>%
  html_table(header = TRUE)

angel <- data.frame(angel)

angel <- slice(angel, 1:(n() - 1)) 
```

## Filtering to Game Date, Total Rebounds

```{r}
baskets_and_boards <- angel %>%
  select('Rk', 'Date','TRB', 'PTS')

```  

## Adding the game by game average for Points and Total Rebounds

```{r}
baskets_and_boards <- baskets_and_boards %>%
  mutate(game_by_game_pts_avg = round(cummean(PTS),1),
         game_by_game_trb_avg = round(cummean(TRB),1))

head(baskets_and_boards)
```

## Adding the 6 Game Mean for Points and Total Rebounds

```{r}
six_game_mean <- function(column) {
  if_else(baskets_and_boards$Rk %% 6 == 0,  cummean(column), NULL)
}

baskets_and_boards <- baskets_and_boards %>%
  mutate(six_game_pts_avg = round(six_game_mean(PTS),1),
         six_game_trb_avg = round(six_game_mean(TRB),1))

baskets_and_boards
```

## Conclusion:

As you can see, Reese's numbers are consistently impressive, which you can see 
on a game-by-game basis in average and individual score form. I have also 
provided an average for both total rebounds and points on a six-game basis. 
These numbers are something to behold, which gives you all the more reason to 
tune in!